Approximating the Optimal State Abstraction

### 2015-10-09 state_abstraction.tex
first results added

>>>>

% --- SECTION: Results! ---
\newpage
\section{Results}

\thm{Lemma}{1}{(Simulation Lemma)}

\thm{Lemma}{2}{Under the model approximate abstraction scheme, an the Q values for the ground MDP will be within $\epsilon$ of the abstract MDP under an arbitrary policy.}

\elem{Proof:} Recall our definition of model approximate abstraction:
\begin{equation}
\forall_{s_1,s_2} \phi(s_1) = \phi(s_2) \rightarrow \forall_{s,a} | T(s,a,s_1) - T(s,a,s_2) | \leq 2\beta
\label{eq:approx_model_abs}
\end{equation}

Sim Lemma says we need T and R to be within $2\beta = \alpha$.

We have our ground MDP: $M_G$, abstract MDP, $M_A$, and noisy ground MDP, $M_{G'}$.

Using a given state abstraction function $\phi$ subject to Equation~\ref{eq:approx_model_abs}, the difference between $T_G$ and $T_{G'}$.

Sim lemma goes through (cause same for $R$).

\thm{Lemma}{3}{Under the optimal Q function approximate abstraction, $\forall_s : |Q_A^*(s,.) - Q_G^*(s,.)| \leq \epsilon$ }

Since for each state, the most you can screw up is by $\epsilon$, since if you don't take $\argmax_a Q^*(s,a)$, then one of the other actions Q functions must have jumped up by at most $\epsilon$, but it's fine because then you're doing no worse then $\epsilon$. It can't have jump mored, because otherwise you wouldn't have compressed on it.
